---
title: "Supplementary sensitivity analyses"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-targets, include=FALSE}
library(targets)
library(gtsummary)
library(flextable)
tar_load(
  c(w3_table, lmm_table, w3_dfs, lmm_dfs, st_trajectory_lmm, model_vo2_w6.5),
  store = here::here("_targets")
)

# Easier printing
pn <- function(val, acc = 0.01) {
  scales::number(val, accuracy = acc)
}

# Pull a formatted estimate (B and 95% CI) from the tidy sensitivity data
pull_lm <- function(df, outcome, term, type = "unadjusted", brackets = FALSE) {
  row <- df[df$outcome == outcome & df$term == term & df$type == type, ]
  txt <- glue::glue(
    "*B* = {pn(row$estimate)}; 95%CI, {pn(row$conf.low)}-{pn(row$conf.high)}"
  )
  if (brackets) {
    txt <- glue::glue(
      "*B* = {pn(row$estimate)} (95%CI, {pn(row$conf.low)}-{pn(row$conf.high)})"
    )
  }
  txt
}
```

# Sensitivity analyses

To confirm that the associations attributed to early screen time are present in
the data itself, and that the trajectory findings are robust to the choice of
modelling framework, we conducted two complementary sensitivity analyses. Both
use the same analysis sample and the same covariate adjustment structure as the
primary latent growth curve models.

## Observed Wave 3 screen time as the exposure

The latent intercept in the growth model is a model-derived quantity estimated
from the full repeated-measures structure and is therefore not identical to the
observed Wave 3 value. As a sensitivity analysis, we replaced the latent
intercept with the *observed* (standardised) Wave 3 screen-time value and
re-estimated the association with each outcome using ordinary least squares
regression (complete cases), with the same covariates as the primary models
(Table \@ref(tab:w3-table)).

```{r w3-results, include=FALSE}
v <- "st_totalz_w3"
```

The pattern of findings was consistent with the primary analysis. Higher
observed Wave 3 screen time was associated with lower cardiorespiratory fitness
(`r pull_lm(w3_dfs, "vo2_w6.5", v)`), higher waist circumference
(`r pull_lm(w3_dfs, "waistcm_w6.5", v)`), higher waist-to-height ratio
(`r pull_lm(w3_dfs, "waist2height_w6.5", v)`), higher body mass index (z-score;
`r pull_lm(w3_dfs, "bmiz_w6.5", v)`), and higher body fat percentage
(`r pull_lm(w3_dfs, "bodyfat_w6.5", v)`). The associations were in the same
direction as, and of comparable magnitude to, those for the latent intercept,
indicating that these findings reflect the observed data rather than the latent
growth-model specification.

\newpage

```{r w3-table}
gtsummary::as_flex_table(w3_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

## Mixed-model (random intercept / random slope) framework

We additionally re-estimated the screen-time trajectory using a conventional
linear mixed model with a random intercept and random slope for time
(`st_totalz ~ time + (time | id)`, fitted with `lme4`), with time coded 0-3
across Waves 3-6 to match the loadings of the latent growth model.

```{r lmm-trajectory, include=FALSE}
lmm <- st_trajectory_lmm$model

fe <- broom.mixed::tidy(lmm, effects = "fixed")
fe_int <- fe[fe$term == "(Intercept)", ]
fe_slope <- fe[fe$term == "time", ]

vc <- as.data.frame(lme4::VarCorr(lmm))
sd_int <- vc$sdcor[vc$grp == "id" & vc$var1 == "(Intercept)" & is.na(vc$var2)]
sd_slope <- vc$sdcor[vc$grp == "id" & vc$var1 == "time" & is.na(vc$var2)]
cor_is <- vc$sdcor[vc$grp == "id" & !is.na(vc$var2)]

# Latent growth model intercept-slope covariance for comparison
lgm_is <- broom::tidy(model_vo2_w6.5$lgcm_adj_fit) %>%
  dplyr::filter(term == "st_intercept ~~ st_slope")
```

The mixed model reproduced the trajectory described by the latent growth model.
The mean trajectory increased over time (slope = `r pn(fe_slope$estimate)`
*z*-units per wave). There was meaningful between-child variation in both the
intercept (SD = `r pn(sd_int)`) and the slope (SD = `r pn(sd_slope)`), and the
intercept and slope were negatively correlated (*r* = `r pn(cor_is)`),
consistent with the negative intercept-slope covariance observed in the latent
growth model (`r pn(lgm_is$estimate)`): children with higher initial screen time
tended to have slower subsequent increases.

To relate the trajectories to later health outcomes in this framework, we
extracted each child's subject-specific (best linear unbiased predictor)
intercept and slope and regressed each outcome on these, using ordinary least
squares with the same covariates as the primary models
(Table \@ref(tab:lmm-table)).

```{r lmm-results, include=FALSE}
vi <- "blup_intercept"
```

As in the primary analysis, the subject-specific intercept was associated with
lower cardiorespiratory fitness (`r pull_lm(lmm_dfs, "vo2_w6.5", vi)`), higher
waist circumference (`r pull_lm(lmm_dfs, "waistcm_w6.5", vi)`), higher
waist-to-height ratio (`r pull_lm(lmm_dfs, "waist2height_w6.5", vi)`), higher
body mass index (z-score; `r pull_lm(lmm_dfs, "bmiz_w6.5", vi)`), and higher body
fat percentage (`r pull_lm(lmm_dfs, "bodyfat_w6.5", vi)`).

We note that subject-specific intercepts and slopes are shrunken towards the
population mean and that this two-stage approach treats them as observed without
propagating the uncertainty in their estimation. These estimates are therefore
conservative, and the consistency of the findings across the latent growth model,
the observed Wave 3 exposure, and the mixed-model framework increases confidence
in the conclusions.

\newpage

```{r lmm-table}
gtsummary::as_flex_table(lmm_table) %>%
  flextable::set_table_properties(layout = "autofit")
```
