---
title: "Supplementary sensitivity analyses"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-targets, include=FALSE}
library(targets)
library(gtsummary)
library(flextable)
tar_load(
  c(
    w3_table, lmm_table, w3_dfs, lmm_dfs, st_trajectory_lmm, model_vo2_w6.5,
    consistent_table, early_table, late_table,
    consistent_dfs, model_dfs, early_dfs, late_dfs, st_wave_plot,
    outcome_skewness, logoutcome_table, logoutcome_dfs
  ),
  store = here::here("_targets")
)

# Easier printing
pn <- function(val, acc = 0.01) {
  scales::number(val, accuracy = acc)
}

# Pull a formatted estimate (B and 95% CI) from the tidy sensitivity data.
# Coerce to a plain data.frame first: some targets are data.tables, whose
# non-standard `[` evaluation would resolve the bare argument names to columns.
pull_lm <- function(df, outcome, term, type = "unadjusted", brackets = FALSE) {
  df <- as.data.frame(df)
  row <- df[df$outcome == outcome & df$term == term & df$type == type, ]
  txt <- glue::glue(
    "*B* = {pn(row$estimate)}; 95%CI, {pn(row$conf.low)}-{pn(row$conf.high)}"
  )
  if (brackets) {
    txt <- glue::glue(
      "*B* = {pn(row$estimate)} (95%CI, {pn(row$conf.low)}-{pn(row$conf.high)})"
    )
  }
  txt
}

# Pull a formatted estimate (B and 95% CI) from a lavaan diagnostic data.frame
pull_lgcm <- function(df, outcome, term = "st_intercept", type = "unadjusted") {
  df <- as.data.frame(df)
  row <- df[df$outcome == outcome & df$term == term & df$type == type, ]
  glue::glue("*B* = {pn(row$coef)}; 95%CI, {pn(row$ci_l)}-{pn(row$ci_u)}")
}

# Pull a back-transformed (multiplicative, per-SD) estimate from a log-scale
# lavaan diagnostic data.frame: exp(coef) is a ratio, 1.00 = no association.
pull_logexp <- function(df, outcome, term = "st_intercept", type = "unadjusted") {
  df <- as.data.frame(df)
  row <- df[df$outcome == outcome & df$term == term & df$type == type, ]
  glue::glue(
    "ratio = {pn(exp(row$coef))}; 95%CI, {pn(exp(row$ci_l))}-{pn(exp(row$ci_u))}"
  )
}
```

# Sensitivity analyses

To confirm that the associations attributed to early screen time are present in
the data itself, and that the trajectory findings are robust to the choice of
modelling framework, we conducted two complementary sensitivity analyses. Both
use the same analysis sample and the same covariate adjustment structure as the
primary latent growth curve models.

## Observed Wave 3 screen time as the exposure

The latent intercept in the growth model is a model-derived quantity estimated
from the full repeated-measures structure and is therefore not identical to the
observed Wave 3 value. As a sensitivity analysis, we replaced the latent
intercept with the *observed* (standardised) Wave 3 screen-time value and
re-estimated the association with each outcome using ordinary least squares
regression (complete cases), with the same covariates as the primary models
(Table \@ref(tab:w3-table)).

```{r w3-results, include=FALSE}
v <- "st_totalz_w3"
```

The pattern of findings was consistent with the primary analysis. Higher
observed Wave 3 screen time was associated with lower cardiorespiratory fitness
(`r pull_lm(w3_dfs, "vo2_w6.5", v)`), higher waist circumference
(`r pull_lm(w3_dfs, "waistcm_w6.5", v)`), higher waist-to-height ratio
(`r pull_lm(w3_dfs, "waist2height_w6.5", v)`), higher body mass index (z-score;
`r pull_lm(w3_dfs, "bmiz_w6.5", v)`), and higher body fat percentage
(`r pull_lm(w3_dfs, "bodyfat_w6.5", v)`). The associations were in the same
direction as, and of comparable magnitude to, those for the latent intercept,
indicating that these findings reflect the observed data rather than the latent
growth-model specification.

\newpage

```{r w3-table}
gtsummary::as_flex_table(w3_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

## Mixed-model (random intercept / random slope) framework

We additionally re-estimated the screen-time trajectory using a conventional
linear mixed model with a random intercept and random slope for time
(`st_totalz ~ time + (time | id)`, fitted with `lme4`), with time coded 0-3
across Waves 3-6 to match the loadings of the latent growth model.

```{r lmm-trajectory, include=FALSE}
lmm <- st_trajectory_lmm$model

fe <- broom.mixed::tidy(lmm, effects = "fixed")
fe_int <- fe[fe$term == "(Intercept)", ]
fe_slope <- fe[fe$term == "time", ]

vc <- as.data.frame(lme4::VarCorr(lmm))
sd_int <- vc$sdcor[vc$grp == "id" & vc$var1 == "(Intercept)" & is.na(vc$var2)]
sd_slope <- vc$sdcor[vc$grp == "id" & vc$var1 == "time" & is.na(vc$var2)]
cor_is <- vc$sdcor[vc$grp == "id" & !is.na(vc$var2)]

# Latent growth model intercept-slope covariance for comparison
lgm_is <- broom::tidy(model_vo2_w6.5$lgcm_adj_fit) %>%
  dplyr::filter(term == "st_intercept ~~ st_slope")
```

The mixed model reproduced the trajectory described by the latent growth model.
The mean trajectory increased over time (slope = `r pn(fe_slope$estimate)`
*z*-units per wave). There was meaningful between-child variation in both the
intercept (SD = `r pn(sd_int)`) and the slope (SD = `r pn(sd_slope)`), and the
intercept and slope were negatively correlated (*r* = `r pn(cor_is)`),
consistent with the negative intercept-slope covariance observed in the latent
growth model (`r pn(lgm_is$estimate)`): children with higher initial screen time
tended to have slower subsequent increases.

To relate the trajectories to later health outcomes in this framework, we
extracted each child's subject-specific (best linear unbiased predictor)
intercept and slope and regressed each outcome on these, using ordinary least
squares with the same covariates as the primary models
(Table \@ref(tab:lmm-table)).

```{r lmm-results, include=FALSE}
vi <- "blup_intercept"
```

As in the primary analysis, the subject-specific intercept was associated with
lower cardiorespiratory fitness (`r pull_lm(lmm_dfs, "vo2_w6.5", vi)`), higher
waist circumference (`r pull_lm(lmm_dfs, "waistcm_w6.5", vi)`), higher
waist-to-height ratio (`r pull_lm(lmm_dfs, "waist2height_w6.5", vi)`), higher
body mass index (z-score; `r pull_lm(lmm_dfs, "bmiz_w6.5", vi)`), and higher body
fat percentage (`r pull_lm(lmm_dfs, "bodyfat_w6.5", vi)`).

We note that subject-specific intercepts and slopes are shrunken towards the
population mean and that this two-stage approach treats them as observed without
propagating the uncertainty in their estimation. These estimates are therefore
conservative, and the consistency of the findings across the latent growth model,
the observed Wave 3 exposure, and the mixed-model framework increases confidence
in the conclusions.

\newpage

```{r lmm-table}
gtsummary::as_flex_table(lmm_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

## Change in screen-time exposure definition across waves

Our total screen-time measure combines three components: television, electronic
games, and computer/other electronic-device use. The television and
electronic-games items were measured identically at all four waves, but the
computer-use item was reworded between Wave 4 and Wave 5 (from time using a
computer to time using other electronic devices/games), so the exposure
definition is not perfectly constant across the trajectory. We conducted two
further sensitivity analyses to assess whether this measurement change affects
our inferences.

As an initial visual check, Figure \@ref(fig:st-wave-plot) shows mean total
screen time at each wave. The trajectory increases steadily across all four
waves with no discontinuity at the Wave 4-5 boundary where the computer/other
item was reworded, and the definition-invariant total (television + electronic
games) follows a parallel progression. This suggests the change in item wording
did not introduce a step change in the measured exposure.

```{r st-wave-plot, fig.width=7, fig.height=4.5, fig.cap="Mean total screen time (minutes/day, with 95% confidence intervals) at each wave, for the full three-component total and the definition-invariant total (television + electronic games). The dashed line marks the Wave 4-5 boundary at which the computer/other component was reworded."}
st_wave_plot
```

### Definition-invariant components only

We first refit the latent growth curve model using a screen-time exposure built
only from the two definition-invariant components (television and electronic
games), excluding the reworded computer/other component
(Table \@ref(tab:consistent-table)).

```{r consistent-results, include=FALSE}
ti <- "st_intercept"
```

The trajectory associations were materially unchanged. Using the
definition-invariant exposure, the trajectory intercept remained associated with
lower cardiorespiratory fitness (`r pull_lgcm(consistent_dfs, "vo2_w6.5", ti)`;
primary model `r pull_lgcm(model_dfs, "vo2_w6.5", ti)`), higher waist
circumference (`r pull_lgcm(consistent_dfs, "waistcm_w6.5", ti)`; primary
`r pull_lgcm(model_dfs, "waistcm_w6.5", ti)`), higher waist-to-height ratio
(`r pull_lgcm(consistent_dfs, "waist2height_w6.5", ti)`; primary
`r pull_lgcm(model_dfs, "waist2height_w6.5", ti)`), higher body mass index
(z-score; `r pull_lgcm(consistent_dfs, "bmiz_w6.5", ti)`; primary
`r pull_lgcm(model_dfs, "bmiz_w6.5", ti)`), and higher body fat percentage
(`r pull_lgcm(consistent_dfs, "bodyfat_w6.5", ti)`; primary
`r pull_lgcm(model_dfs, "bodyfat_w6.5", ti)`). Estimates were consistent in
direction and similar in magnitude to the primary full-component model.

\newpage

```{r consistent-table}
gtsummary::as_flex_table(consistent_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

### Early (Waves 3-4) and later (Waves 5-6) periods modelled separately

We then modelled the two definition regimes separately, using the average
standardised screen time within the early period (Waves 3-4, original
computer-item definition) and within the later period (Waves 5-6, revised
definition) as the exposure in ordinary least squares models with the same
covariates (Tables \@ref(tab:early-table) and \@ref(tab:late-table)).

```{r period-results, include=FALSE}
te <- "st_earlyz"
tl <- "st_latez"
```

Associations were consistent in direction across the two periods. For example,
both the early-period exposure (original definition) and the later-period
exposure (revised definition) were associated with lower cardiorespiratory
fitness (Waves 3-4 `r pull_lm(early_dfs, "vo2_w6.5", te)`; Waves 5-6
`r pull_lm(late_dfs, "vo2_w6.5", tl)`), higher waist circumference
(Waves 3-4 `r pull_lm(early_dfs, "waistcm_w6.5", te)`; Waves 5-6
`r pull_lm(late_dfs, "waistcm_w6.5", tl)`), and higher body fat percentage
(Waves 3-4 `r pull_lm(early_dfs, "bodyfat_w6.5", te)`; Waves 5-6
`r pull_lm(late_dfs, "bodyfat_w6.5", tl)`). Taken together with the
definition-invariant analysis, these results indicate that the change in the
computer-item definition between Waves 4 and 5 does not materially affect our
inferences.

\newpage

```{r early-table}
gtsummary::as_flex_table(early_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r late-table}
gtsummary::as_flex_table(late_table) %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

## Right-skewed outcomes modelled on the natural-log scale

Several of the standalone health outcomes are right-skewed, which can affect the
normality of model residuals and the validity of the standard errors in the
primary models (which are fit in the outcomes' natural units). As a sensitivity
analysis we identified the materially skewed outcomes from the data and re-fit
them on the natural-log scale.

Selection was data-driven: we computed the marginal skewness of every continuous
outcome on the analysis sample (Table \@ref(tab:skewness-table)) and re-fit, on
the log scale, those that were at least moderately right-skewed (skewness > 0.8)
and strictly positive. This flagged
`r nrow(as.data.frame(logoutcome_dfs)[!duplicated(as.data.frame(logoutcome_dfs)$outcome), ])`
outcomes: triglycerides, waist-to-height ratio, waist circumference, glycoprotein
acetyls, the ApoB/ApoA1 ratio, and glucose. The already-standardised z-score
outcomes (BMI, blood pressure) and the composite risk score were not eligible,
and the remaining outcomes were not materially skewed. Each flagged outcome was
re-estimated with the same latent growth curve specification and covariates as
the primary models; because the exposure is standardised, the log-scale
coefficients back-transform to a multiplicative change (a ratio) in the outcome
per 1 SD of screen time (Table \@ref(tab:logoutcome-table)).

```{r skewness-table}
os <- as.data.frame(outcome_skewness)
os$skewness <- pn(os$skewness, 0.01)
os$min <- pn(os$min, 0.01)
os$median <- pn(os$median, 0.01)
os$max <- pn(os$max, 0.01)
os$log_flag <- ifelse(os$log_flag, "Yes", "No")
flextable::flextable(
  os[, c("outcome", "n", "min", "median", "max", "skewness", "log_flag")]
) |>
  flextable::set_header_labels(
    outcome = "Outcome", skewness = "Skewness",
    log_flag = "Log-transformed"
  ) |>
  flextable::set_caption(
    "Marginal skewness of candidate continuous outcomes on the analysis sample. Outcomes with skewness > 0.8 and strictly positive values were re-fit on the log scale."
  ) |>
  flextable::set_table_properties(layout = "autofit")
```

\newpage

The findings were consistent with the primary analysis. For example, the
trajectory intercept remained positively associated with waist circumference
(back-transformed `r pull_logexp(logoutcome_dfs, "waistcm_w6.5")`; primary
natural-unit `r pull_lgcm(model_dfs, "waistcm_w6.5")`) and waist-to-height ratio
(`r pull_logexp(logoutcome_dfs, "waist2height_w6.5")`), while there remained no
clear association with triglycerides
(`r pull_logexp(logoutcome_dfs, "trigly_w6.5")`), glycoprotein acetyls
(`r pull_logexp(logoutcome_dfs, "glycoprotein_w6.5")`), the ApoB/ApoA1 ratio
(`r pull_logexp(logoutcome_dfs, "ApoBA1_ratio_w6.5")`), or glucose
(`r pull_logexp(logoutcome_dfs, "glucose_w6.5")`). Modelling these outcomes on
the log scale did not change the statistical significance of any association
relative to the primary models, and the direction of every non-null effect was
unchanged.

\newpage

```{r logoutcome-table}
logoutcome_table
```
